The pollination trade-off

### 2018-08-22 paper/supp-info.Rmd
Add variable importance table
Issue #5

>>>>

```{r table-variable-importance, results='asis'}
drake::loadd(model_formula_ranking)

# get the terms in the models
terms <- model_formula_ranking$aggregated$fixed_formula %>%
  stringr::str_remove("pollen_gain ~  ") %>%
  stringr::str_split(stringr::fixed(" + ")) %>%
  unlist() %>%
  unique() 
# remove the null model
terms <- terms[terms != "1"]

model_weights <- model_formula_ranking$by_model_set %>%
  dplyr::filter(scale == "community") %>%
  dplyr::group_by(pollen_category) %>%
  dplyr::mutate(likelyhood = get_likelyhoods(delta_AIC_median), 
                weight = get_weights(likelyhood))

crosses <- purrr::cross2(terms, c("conspecific", "heterospecific"))
crosses %>%
  purrr::map(~model_weights$weight[stringr::str_detect(model_weights$fixed_formula, .[[1]]) & model_weights$pollen_category == .[[2]]]) %>%
  purrr::map(sum) %>%
  purrr::map2_df(crosses, 
              ~ dplyr::data_frame(
                var = .y[[1]],
                pollen_category = .y[[2]], 
                importance = .x)
              ) %>%
  dplyr::mutate(importance = round(importance, digits = 3)) %>%
  dplyr::rename(term = var) %>%
  humanize() %>%
  tidyr::spread(pollen_category, importance) %>%
  dplyr::arrange(dplyr::desc(conspecific), heterospecific) %>%
  dplyr::rename(`fixed effect`= term, 
                `conspecific pollen` = conspecific, 
                `heterospecific pollen` = heterospecific) %>%
  knitr::kable(caption = "Relative variable impotance of the four vaariables included as fixed effects. Variable importance was calculated as the sum of the median Akaike weights (Table \\ref{tab:table-aic-fixed-models}) of each candidate model set that includes the variable.", 
               booktabs = TRUE) %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::add_header_above(c(" ", "variable importance" = 2))
```
